---
title: "Project 2"
author: "Austin Lee"
date: "2023-04-20"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Helper packages
library(tidyverse)
library(reshape2) # for data shaping
library(dplyr) # for data manipulation
library(ggplot2) # for awesome graphics
# Modeling process packages
library(rsample) # for resampling procedures
library(caret) # for resampling and model training
# Model interpretability packages
library(vip) # variable importance

```{r}
# Load the California Housing dataset
url <- "https://raw.githubusercontent.com/ageron/handson-ml/master/datasets/housing/housing.csv"
Housing <- read.table(url, header = TRUE, sep = ",")

# View the dataset
View(Housing)

# Install the ISLR package
install.packages("ISLR")

# Load the ISLR package
library(ISLR)
```


1. 
```{r}
 
# Load the California Housing dataset
url <- "https://raw.githubusercontent.com/ageron/handson-ml/master/datasets/housing/housing.csv"
Housing <- read.table(url, header = TRUE, sep = ",")

# Install the rsample package
install.packages("rsample")

# Load the rsample package
library(rsample)

# Split the data into training and testing sets using rsample
set.seed(123)
split <- initial_split(Housing, prop = 0.7, strata = "ocean_proximity")
train <- training(split)
test <- testing(split)

# Verify that the training and testing sets were created correctly
nrow(train) + nrow(test) == nrow(Housing)

model <- lm(median_house_value ~ median_income + total_rooms + population, data = Housing)
summary(model)

library(ggplot2)

ggplot(data = Housing, aes(x = median_income, y = median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  scale_y_continuous(labels = scales::dollar_format()) +
  labs(x = "Median Income", y = "Median House Value ($)", title = "Relationship between Median Income and Median House Value")
```


3. 
model 2: 
```{r}
# Train the model2
model2 <- lm(median_house_value ~ median_income + population, data = Housing)

# Print the summary of the model
summary(model2)
```

model 3:
```{r}
# Load the California Housing dataset
url <- "https://raw.githubusercontent.com/ageron/handson-ml/master/datasets/housing/housing.csv"
Housing <- read.table(url, header = TRUE, sep = ",")

# Train the model3
model3 <- lm(median_house_value ~ median_income  + population + housing_median_age, data = Housing)

# Print the summary of the model
summary(model3)
```


4. 
```{r}
library(caret)
library(mlr)

# Define the models
model1 <- lm(median_house_value ~ median_income, data = Housing)
model2 <- lm(median_house_value ~ median_income  + population, data = Housing)
model3 <- lm(median_house_value ~ median_income + population + housing_median_age, data = Housing)

# Define the cross-validation method
ctrl <- trainControl(method = "cv", number = 5)
```



```{r}
# Update caret package to the latest version
install.packages("caret", dependencies = TRUE)
library(caret)
# Verify the column names to ensure they match
colnames(Housing)
```









5. 
```{r}
# Load required libraries
library(ggplot2)
library(gridExtra)

# Train Simple Linear Model (model1)
model1 <- lm(median_house_value ~ median_income, data=Housing)

# Pair of plots for Simple linear model (model1)
p1 <- ggplot(data=model1, aes(x=.fitted, y=.resid)) +
  geom_point() +
  ggtitle("Residuals vs. Fitted Values") +
  xlab("Fitted values") +
  ylab("Residuals") 

p2 <- ggplot(data=model1, aes(sample=.resid)) +
  geom_qq() +
  ggtitle("Normal Q-Q Plot") 

# Arrange the two plots together using grid.arrange() function
grid.arrange(p1, p2, ncol=2)

# Train Multiple Linear Model (model3)
model3 <- lm(median_house_value ~ median_income  + population + housing_median_age, data=Housing)

# Pair of plots for Multiple linear model (model3)
p1 <- ggplot(data=model3, aes(x=.fitted, y=.resid)) +
  geom_point() +
  ggtitle("Residuals vs. Fitted Values") +
  xlab("Fitted values") +
  ylab("Residuals") 

p2 <- ggplot(data=model3, aes(sample=.resid)) +
  geom_qq() +
  ggtitle("Normal Q-Q Plot") 

# Arrange the two plots together using grid.arrange() function
grid.arrange(p1, p2, ncol=2)
```

------------
For the Simple linear model (model1):

Independence among residuals: The residuals are randomly scattered around the horizontal axis in the "Residuals vs. Fitted Values" plot, indicating that there is no clear pattern in the residuals. Thus, the assumption of independence among residuals is likely to be met.

Normality of residuals: The residuals follow a straight line in the "Normal Q-Q Plot" plot, indicating that the assumption of normality of residuals is likely to be met.

Equal variance for residuals: The residuals are randomly scattered around the horizontal axis in the "Residuals vs. Fitted Values" plot, indicating that there is no clear pattern in the residuals. Thus, the assumption of equal variance for residuals is likely to be met.

For the Multiple linear model (model3):

Independence among residuals: The residuals are randomly scattered around the horizontal axis 



